External Prior Guided Internal Prior Learning for Real Noisy Image Denoising

### 2016-11-11 CVPR2017_Review_Unified.tex
add

\begin{figure*}\vspace{-0.1in}
\centering
\includegraphics[width=0.7\linewidth]{Flowchart.png}
\vspace{-3mm}
\caption{Flowchart of the proposed external prior guided internal prior learning and real noisy image denoising framework.
}
\vspace{-3mm}
\label{fig2}
\end{figure*}

@@

In the literature of real noisy image denoising, most denoising methods \cite{Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016,neatimage} use explicit statistical models, such as Gaussian or mixture of Gaussians to model the noise, and learn image priors from either external data or the noisy image itself to remove noise. However, the noise in real-world noisy images is much more complex and hard to be modeled by simple analytical distributions. In this paper, we proposed a simple yet effective solution for real noisy image denoising without explicitly assuming certain noise models. Specifically, we firstly learned image priors of Gausian Mixture Model from external clean images, and then employ the learned external priors to guide the learning of internal latent priors from the given noisy image. The learned hybrid orthogonal dictionary are simutaneously utilized in real noisy image denoising. Experiments on two real noisy image datasets demonstrate that our proposed method achieved much better performance than state-of-the-art image denoising methods.

>>>>

\begin{figure*}\vspace{-0.1in}
\centering
\includegraphics[width=0.35\linewidth]{Flowchart.png}
\vspace{-3mm}
\caption{Flowchart of the proposed external prior guided internal prior learning and real noisy image denoising framework.
}
\vspace{-3mm}
\label{fig2}
\end{figure*}

@@

The noise in real-world noisy images is much more complex than additive white Gaussian noise and hard to be modeled by simple analytical distributions such as Gaussian or mixture of Gaussians. In this paper, we proposed a simple yet effective solution for real noisy image denoising without explicitly assuming certain noise models. Specifically, we firstly learned image priors of Gausian Mixture Model from external clean images, and then employ the learned external priors to guide the learning of internal latent priors from the given noisy image. The learned hybrid orthogonal dictionary are simutaneously utilized in real noisy image denoising. Experiments on two real noisy image datasets demonstrate that our proposed method achieved much better performance than state-of-the-art image denoising methods.
